Stat 400 Project

### 2021-12-03 Stat 400 proj.Rmd
Trying to fix merge conflict
fix merge conflict

#Function for deciding if infections occured
#BUG -- If the mean_crit_dist is small, all infections go away!!
#BUG -- Sometimes d is NA, I assume it's when indv goes off map. 
infection_status <- function(state, mean_crit_dist,day_r,rt){

@@

      if(d <= crucial_distance){
        new_status[j] <- 'I'

        newly_infected <- c(newly_infected, j)
      }else{new_status[j] <- 'S'}

@@

      #if day is past recovery time, set to recovered
      else if(day_r >= rt){
        new_status[j] <- 'R'
      }

      else{
        new_status[j] <- 'S'
      }
>>>>>>> infection status update
    }
  }

@@

    updated_positions <- update_coords(initial_data, change)#, x_dim, y_dim)x_dim,y_dim not parameters
    # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
    updated_state <- cbind(updated_positions, initial_data[,3])
    new_status <- infection_status(updated_state, 2,i,14)
    end_day[[i]] <- cbind(updated_positions, new_status)
    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)

@@

    end_day[[i]] <- cbind(updated_positions, new_status)

    }
  }
  return(end_day[[3]])
}

>>>>

#Function for deciding if infections occured
#BUG -- If the mean_crit_dist is small, all infections go away!!
#BUG -- Sometimes d is NA, I assume it's when indv goes off map. 
infection_status <- function(state, mean_crit_dist){

@@

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }
      else{new_status[j] <- 'S'}

@@

      else{
        new_status[j] <- 'S'
      }
    }
  }

@@

      updated_positions <- update_coords(initial_data, change)#, x_dim, y_dim)x_dim,y_dim not parameters
      # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      updated_state <- cbind(updated_positions, initial_data[,3])

      new_status <- infection_status(updated_state, 2)

      end_day[[i]] <- cbind(updated_positions, new_status)
    }
    else{
      step_size <- get_step_length(initial_data, x_dim, y_dim)
      direction <- get_step_direction(step_size)
      change <- get_delts(step_size, direction)

@@

      end_day[[i]] <- cbind(updated_positions, new_status)
    }
  }
  return(end_day[[3]])
}
